Extended Data

### 2021-10-05 doc/manuscript/Dow_manuscript_Nature.Rmd
add "consistently" for clarity
set title
@camerondow35 , I think we should go with "annual woody productivity" rather than "annual increments" in the title. The latter is more precise, but I think the former is more meaningful.

**Title:** Warmer spring temperatures in temperate deciduous forests advance the timing of tree growth but have little effect on annual woody productivity */annual increments*

@@

Despite remaining uncertainties, our findings contribute substantially to a broader picture of the influence of spring temperatures on forest ecosystem function. 
Warm spring temperatures result in earlier leaf-out (Fig. `r DOY_timing`)[@jeong_phenology_2011], an earlier start to net C sequestration[@keenan_net_2014], and, as shown here, earlier initiation of stem growth (Figs. `r schematic_summary`, `r EDF_pheno_Tmax_climwin`).
Yet, an earlier start to the growing season is not associated with a longer peak growing season or increased growth (Figs. `r schematic_summary`, `r tree_rings`), presumably because stem diameter growth is curtailed by C sink limitation[@zani_increased_2020] or drought[@zhang_drought_2021;@dorangeville_drought_2018;@helcoski_growing_2019].

>>>>

**Title:** Warmer spring temperatures in temperate deciduous forests advance the timing of tree growth but have little effect on annual woody productivity

@@

Despite remaining uncertainties, our findings contribute substantially to a broader picture of the influence of spring temperatures on forest ecosystem function. 
Warm spring temperatures result in earlier leaf-out (Fig. `r DOY_timing`)[@jeong_phenology_2011], an earlier start to net C sequestration[@keenan_net_2014], and, as shown here, earlier initiation of stem growth (Figs. `r schematic_summary`, `r EDF_pheno_Tmax_climwin`).
Yet, an earlier start to the growing season is not consistently associated with a longer peak growing season or increased growth (Figs. `r schematic_summary`, `r tree_rings`), presumably because stem diameter growth is curtailed by C sink limitation[@zani_increased_2020] or drought[@zhang_drought_2021;@dorangeville_drought_2018;@helcoski_growing_2019].
